Hemispheric Lateralization in ICH

### 2023-05-19 code/dataAnalysis/02analysis.qmd
Update 02analysis.qmd

library(tidyverse)
# library(gt) # Fancy tables
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
library(stringr)
library(qs)
library(glue)
library(scales) # Nicer labeling functions
library(ggmosaic) # Mosaic plots with ggplot
library(ggplot2)
library(ggpattern) # Pattern fills in ggplot
library(patchwork) # Combine plots nicely
library(systemfonts) ## use custom fonts (need to be installed on your OS)
library(scico) ## scico color palettes(http://www.fabiocrameri.ch/colourmaps.php) in R
library(ggtext) ## add improved text rendering to ggplot2
library(ggforce) ## add missing functionality to ggplot2
library(ggdist) ## add uncertainity visualizations to ggplot2
library(viridis)

@@

>>>>

library(tidyverse)
# library(gt) # Fancy tables
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
library(stringr)
library(qs)
library(glue)
library(scales) # Nicer labeling functions
library(ggmosaic) # Mosaic plots with ggplot
library(ggplot2)
library(ggpattern) # Pattern fills in ggplot
library(patchwork) # Combine plots nicely
library(systemfonts) ## use custom fonts (need to be installed on your OS)
library(scico) ## scico color palettes(http://www.fabiocrameri.ch/colourmaps.php) in R
library(ggtext) ## add improved text rendering to ggplot2
library(ggforce) ## add missing functionality to ggplot2
library(ggdist) ## add uncertainity visualizations to ggplot2
library(viridis)
library(dagitty)

@@

dag {
bb="0,0,1,1"
"Disease Severity" [adjusted,pos="0.152,0.791"]
"Early WLST" [adjusted,pos="0.326,0.215"]
"Functional Outcome" [outcome,pos="0.916,0.455"]
"ICH Laterality" [exposure,pos="0.070,0.455"]
Age [adjusted,pos="0.253,0.858"]
Comorbidities [adjusted,pos="0.380,0.903"]
Neurosurgery [adjusted,pos="0.736,0.148"]
Rehabilitation [latent,pos="0.849,0.703"]
"Disease Severity" -> "Early WLST"
"Disease Severity" -> "Functional Outcome"
"Disease Severity" -> Neurosurgery
"Disease Severity" -> Rehabilitation
"Early WLST" -> "Functional Outcome"
"ICH Laterality" -> "Early WLST"
"ICH Laterality" -> "Functional Outcome"
"ICH Laterality" -> Neurosurgery
Age -> "Functional Outcome"
Age -> Neurosurgery
Age -> Rehabilitation
Comorbidities -> "Functional Outcome"
Comorbidities -> Neurosurgery
Comorbidities -> Rehabilitation
Neurosurgery -> "Functional Outcome"
Rehabilitation -> "Functional Outcome"
}
